\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
  {Project Manager and Applied Research and Development}{Mar 2020 - Apr 2023}
  {\href{https://www.linkedin.com/company/sunyar/}{Sunyar Co}}{}
    \resumeItemListStart
      \resumeItem{Satellite and Wireless Communication System Designing}
      {Developed real-time satellite and wireless communication systems for various projects, encompassing the design and implementation of systems such as the GMR satellite receiver, GPU-Based Software Defined Radio (SDR), DVBS, DVBS2, and DVBS2X receivers, IDIRECT satellite receiver, and a customized communication link for video transmission.The Design meets specific requirements and employed GPUs or FPGAs based on project demands.}
      \resumeItem{Software Developer}
      {Experienced in designing real-time voice software using Qt or C++, involving the implementation of various processes, system controls, and GUI management.}   
      \resumeItem{Hardware Developer (GPU)}
      {Implemented the physical layer and data link layer of communication links, encompassing various types of channel coding, decoding, interleaving, scrambling, and source encoding/decoding, in both the transmitter and receiver sides.}              
      \resumeItem{Hardware Developer (FPGA)}
      {Implemented SDRs and satellite receivers, Additionally, implemented combined GPU-FPGA-based systems.} 
      \resumeItem{AI-Based System Developer}
      {Designed and implemented deep learning based automatic modulation recognition system} 
      \resumeItem{Other Responsibilities}
      {Established this company and Managed more than ten projects in about three years.} 
      \resumeItemListEnd

    \resumeSubheading
      {Project Manager and Applied R\&D}{Sep 2018 - Mar 2020}
      {\href{https://iranlabexpo.ir/en/company/2983/Farateif-Pouya-Technology}{Farateif Pouya Technology}}{}
      \resumeItemListStart
        \resumeItem{System Designer}
          {Developed diverse communication systems tailored for implementation in FPGAs and GPUs, employing both fixed-point and floating-point architectures to meet specific requirements.}
        \resumeItem{Senior Software and Hardware Developer}
          {Implemented CPU and GPU-based projects utilizing Qt, C++, and CUDA for efficient real-time data processing. Additionally, designed GPU-FPGA based projects employing CUDA, system generator, and VHDL to leverage the power of parallel processing.}
        \resumeItem{Tutor}
          {Mentored and trained over ten individuals in the field of software and hardware engineering, in addition to fulfilling other responsibilities.}
      \resumeItemListEnd

    \resumeSubheading
      {Software and Hardware Developer}{Feb 2015 - Sep 2018}
      {\href{https://iranlabexpo.ir/en/company/2983/Farateif-Pouya-Technology}{Farateif Pouya Technology}}{}
        \resumeItemListStart
          \resumeItem{C++ and Qt Developer}
          {Developed projects using Qt, C++, and occasionally C\# to handle real-time data processing, data visualization, and GUI management.}
          \resumeItem{FPGA Developer}
          {Executed multiple projects utilizing Xilinx FPGAs with the System Generator tool and occasionally VHDL to construct advanced wideband communication systems.}
        \resumeItemListEnd

    \resumeSubheading
      {Communication System Advisor}{Aug 2018 - Nov 2018}
      {\href{https://www.linkedin.com/company/sepehran-company/}{Sepehran}}{}
      \resumeItemListStart
        \resumeItem{FPGA-Based System Advisor}
          {Addressed longstanding challenges that persisted within the company for over a year by successfully implementing an enhanced anti-jamming algorithm as a subblock for their radar project.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd